%-----------PROJECTS-----------%
\section{About Me}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Certifications}}{}
    \resumeItemListStart
        \resumeItem {Since the beginning of 2024, I have spent my spare time pursuing security certifications and focusing on rewriting some of my personal projects to C\# in order to port them to Windows.  I am currently studying for the CASP+ and plan to get the PenTest+ after that.}
        \resumeItem{Once I am done with those CompTIA security certifications I will be moving on to the ISC$^2$ certifications.}
        \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Software Development}}{\href{https://go.dev/}{Golang} | C | \href{https://gitlab.com/gibersonja}{gitlab.com/gibersonja}}
    \resumeItemListStart
        \resumeItem{In addition to this, I also enjoy working on side projects that involve programming. For the last few years it has been Go for my language of choice for most tasks personal and professional.}
        \resumeItem{Lately I have been working on implementing some of the most common internet protocols from the RFC documentation. I have made my way through \href{https://gitlab.com/gibersonja/dhcp-server/-/blob/main/dhcp-server.go?ref_type=heads}{DHCP}, \href{https://gitlab.com/gibersonja/internet-protocol-standards/-/blob/main/STD5-RFC1112-ICMP/icmp.go?ref_type=heads}{ICMP}, and partly through \href{https://gitlab.com/gibersonja/internet-protocol-standards/-/blob/main/STD33-RFC1350-TFTP/tftp.go?ref_type=heads}{TFTP}. The next protocols I will tackle are FTP and SNMP.}
        \resumeItem{I find that this is not only a fun exercise but also an invaluable learning experience which greatly exceeds just reading the documentation alone. You can see what I have been working on: \href{https://gitlab.com/gibersonja}{gitlab} page.}
    \resumeItemListEnd

    \resumeProjectHeading
%    {\textbf{PLCs}}{}
%    \resumeItemListStart
%        \resumeItem{To expand my knowledge of Industrial Control Systems (ICS) I am currently working through the PLC classes \textit{\href{https://www.udemy.com/course/plc_programming}{Applied Logic}} and \textit{\href{https://www.udemy.com/course/hmi-scada/}{Process Visualization}}}
%    \resumeItemListEnd
\resumeSubHeadingListEnd